Enforced Invariant Confluence

### 2018-04-30 doc/paper/sections/invariant_confluence.tex
Added more of a warmup to section 2.

\section{Invariant Confluence}\seclabel{InvariantConfluence}
Informally, a replicated object is \defword{\invariantconfluent{}} with respect
to an invariant if every replica of the object is guaranteed to satisfy the
invariant despite the possibility of different replicas being concurrently
modified or merged together~\cite{bailis2014coordination}. In this section, we
make this informal notion of \invariantconfluence{} precise. We begin by
introducing our system model of replicated objects and then present a formal
definition of \invariantconfluence{}.

\subsection{System Model}
A \defword{distributed object} $O = (S, \join)$ consists of a set $S$ of states
and a binary merge operator $\join: S \times S \to S$ which merges two states
into one. A \defword{transaction} $t: S \to S$ is a function which maps one
state to another. An \defword{invariant} $I$ is a subset of $S$.  Notationally,
we write $I(s)$ to denote that $s$ satisfies the invariant (i.e.  $s \in I$)
and $\lnot I(s)$ to denote that $s$ does not satisfy the invariant (i.e. $s
\notin I$).

>>>>

\section{Invariant Confluence}\seclabel{InvariantConfluence}
Informally, a replicated object is \defword{\invariantconfluent{}} with respect
to an invariant if every replica of the object is guaranteed to satisfy the
invariant despite the possibility of different replicas being concurrently
modified or merged together~\cite{bailis2014coordination}. In this section, we
make this informal notion of \invariantconfluence{} precise.

We begin by introducing our system model of replicated objects in which a
distributed object and accompanying invariant is replicated across a set of
servers. Clients send transactions to servers, and a server executes a
transaction so long as it maintains the invariant. Servers execute
transactions without coordination, but to avoid state divergence, servers
periodically gossip with one another and merge their replicas.
%
After we introduce the system model, we present a formal definition of
\invariantconfluence{}.

\subsection{System Model}

A \defword{distributed object} $O = (S, \join)$ consists of a set $S$ of states
and a binary merge operator $\join: S \times S \to S$ which merges two states
into one. A \defword{transaction} $t: S \to S$ is a function which maps one
state to another. An \defword{invariant} $I$ is a subset of $S$.  Notationally,
we write $I(s)$ to denote that $s$ satisfies the invariant (i.e.  $s \in I$)
and $\lnot I(s)$ to denote that $s$ does not satisfy the invariant (i.e. $s
\notin I$).
